gij bent 2

### 2025-08-19 paper/paper.qmd
typo fix

It is essential to recognize that the widespread changes observed across entire populations ultimately stem from changes that begin within individuals. While linguistic changes may eventually become collective phenomena, their origins lie in the minds and speech of individual speakers. This is way both from a usage-based and a cognitive-linguistic perspective the individual should be the primary unit of linguistic analysis where possible. Recent studies into individual variation in language use reveal that linguistic behavior is not uniformly progressive or conservative, either within individuals or among groups [Nevalainen, Raumolin-Brunberg, and Mannila 2011 TODO]. While later-born authors often show more progressive tendencies, there is notable individual variation even within generational cohorts [Petré and Van de Velde 2018 TODO]. There is also variation in the language-internal factors influencing language change. While most language-internal factors are broadly shared, less influential factors reveal personal differences in usage [Fonteyn and Nini 2020 TODO]. Moreover, some individuals are more adaptable to linguistic change over their lifetimes, while others remain stable or even deviate in the opposite direction [Fonteyn and Petré 2022 TODO]. Personality traits also play a role, affecting how individuals adopt or evaluate new linguistic features [Guy 2013; Zenner, Kristiansen, and Geeraerts 2016; Van den Stock et al. 2024 TODO].

>>>>

It is essential to recognize that the widespread changes observed across entire populations ultimately stem from changes that begin within individuals. While linguistic changes may eventually become collective phenomena, their origins lie in the minds and speech of individual speakers. This is why both from a usage-based and a cognitive-linguistic perspective the individual should be the primary unit of linguistic analysis where possible. Recent studies into individual variation in language use reveal that linguistic behavior is not uniformly progressive or conservative, either within individuals or among groups [Nevalainen, Raumolin-Brunberg, and Mannila 2011 TODO]. While later-born authors often show more progressive tendencies, there is notable individual variation even within generational cohorts [Petré and Van de Velde 2018 TODO]. There is also variation in the language-internal factors influencing language change. While most language-internal factors are broadly shared, less influential factors reveal personal differences in usage [Fonteyn and Nini 2020 TODO]. Moreover, some individuals are more adaptable to linguistic change over their lifetimes, while others remain stable or even deviate in the opposite direction [Fonteyn and Petré 2022 TODO]. Personality traits also play a role, affecting how individuals adopt or evaluate new linguistic features [Guy 2013; Zenner, Kristiansen, and Geeraerts 2016; Van den Stock et al. 2024 TODO].
